P4IRS: An Intermediate Representation and Compiler for Parallel and Performance-Portable Particle Simulations

### 2025-04-30 sage_latex_template/manuscript.tex
Minor
Signed-off-by: Rafael Ravedutti <rafael.r.ravedutti@fau.de>

>>>>

\begin{figure*}[htb]
  \centering
  \includegraphics[width=0.75\textwidth]{pairs_architecture.pdf}
  \caption{\RMchange{P4IRS architecture. The user specifies the Particle Computations to be performed, which are compiled to the Python AST and further mapped to the P4IRS IR. Optimization Choices and Simulation Setup methods are used to determine which internal kernels are utilized, and the P4IRS IR is constructed in-place for the Internal Particle Optimization Kernels based on the inputs. Many Compilation Passes are performed to transform the P4IRS IR before triggering the Code Generator, which generates the Optimized Kernels, Data Structures and the PairsSimulation interface class. When whole-program generation is not used, a backend Simulation Code is required, and it uses the PairsSimulation interface to call P4IRS generated kernels. The final Binary is then generated with any backend compiler the user chooses (i.e., GCC, CLANG, ...), and it must be linked with the Runtime Library. The Runtime Library uses the P4IRS Metadata structure to handle different particle data structures and adapt to different simulations.}}
  \label{fig:features}
\end{figure*}
